---
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    keep_tex: yes
    dev: tikz
bibliography: bibliography.bib
csl: apa-5th-edition.csl
# csl: cambridge-journal-of-economics.csl
# documentclass: book
classoption: twoside
geometry: 
    top = 25mm,
    left=25mm,
    right=25mm,
    bottom=25mm,
    paperwidth=170mm, 
    paperheight=240mm
urlcolor: black
linkcolor: red
fontsize: 10pt
font-family: times
header-includes:
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \onehalfspacing
- \usepackage{chngcntr}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \counterwithin{equation}{section}
- \counterwithin{footnote}{section}
# - \counterwithin{page}{section}
- \usepackage{subfig}
- \usepackage{float}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \renewcommand{\thepage}{(\thesection):\arabic{page}}
- \newcommand{\onlythepage}{\arabic{page}}
- \newcommand*{\secref}[1]{Section~\ref{#1}}
- \raggedbottom
# - \setlength\parskip{2.5em}
# - \pdfpagewidth 140mm
# - \pdfpageheight 170mm
---

```{r global_options, include=FALSE}

sapply(c("reshape2", "quantmod", "Hmisc", "mFilter", "xtable", "plotrix", "networkD3",
         "Formula", "knitr", "reshape", "plm", "countrycode", "tidyr", "dplyr", "eurostat",
         "plyr", "foreign","ecb", "tidyverse", "stringr", "rstudioapi", "ggplot2", "corpcor",
         "perturb","data.table", "rowr", "statsDK", "date", "kableExtra",
         "readxl", "OECD", "viridis", "fpp", "rsdmx", "roll", "scales", "randomcoloR",
         "grid", "cowplot"), require, character.only = TRUE)

options(knitr.kable.NA = '', knitr.table.format = "latex")

#########################################################################
# Set knitr chunk options
#########################################################################

opts_chunk$set(fig.path = 'figures/',
               echo = FALSE, 
               message = FALSE, 
               warning = FALSE, 
               fig.align = "center", 
               fig.width = 5,
               fig.pos = 'H',
               as.is = TRUE,
               include = TRUE,
               cache = TRUE)

#########################################################################
#########################################################################
# Set active working directory to file location
# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))


#########################################################################
#########################################################################
# Create some useful file paths
# 

data_path <- "/Users/robertayretonbaileysmith/OneDrive - Aalborg Universitet/AAU/07 Supervision Work/00 Materials/Rmarkdown projects/data"
image_path <- "/Users/robertayretonbaileysmith/OneDrive - Aalborg Universitet/AAU/07 Supervision Work/00 Materials/Rmarkdown projects/images"


#########################################################################
#########################################################################
# Set up some extra features for plots that will be used later

plot_line_width = 0.85

#########################################################################
# Set colour palettes
#########################################################################

blackpalette <- c("0, 0, 0",
                  "125, 125, 125",
                  "75, 75, 75",
                  "225, 30, 0")
bluepalette <- c("0, 50, 130",
                 "0, 170, 255",
                 "0, 200, 255",
                 "0, 55, 255")
redpalette <- c("255, 45, 0",
                "255, 200, 0",
                "255, 155, 0",
                "255, 100, 0")

blackpalette_five <- c("0, 0, 0",
                       "185, 190, 200",
                       "115, 115, 115",
                       "75, 75, 75",
                       "225, 30, 0")
bluepalette_five <- c("0, 50, 130",
                      "0, 150, 255",
                      "0, 175, 255",
                      "0, 200, 255",
                      "0, 55, 255")
redpalette_five <- c("255, 45, 0",
                     "255, 200, 0",
                     "255, 175, 0",
                     "255, 145, 0",
                     "255, 100, 0")

blackpalette_six <- c("0, 50, 130",
                      "0, 0, 0",
                      "185, 190, 200",
                      "115, 115, 115",
                      "75, 75, 75",
                      "225, 30, 0")
bluepalette_six <- c("0, 50, 130",
                     "0, 100, 255",
                     "0, 130, 255",
                     "0, 165, 255",
                     "0, 200, 255",
                     "0, 55, 255")
redpalette_six <- c("255, 45, 0",
                    "255, 240, 0",
                    "255, 210, 0",
                    "255, 180, 0",
                    "255, 155, 0",
                    "255, 100, 0")


bluepalette <- c("0, 50, 130",
                 "0, 170, 255",
                 "0, 200, 255",
                 "0, 55, 255")
redpalette <- c("255, 45, 0",
                "255, 200, 0",
                "255, 155, 0",
                "255, 100, 0")

randompalette <- c("91, 163, 111",
                   "84, 135, 158",
                   "76, 99, 143",
                   "204, 157, 2",
                   "156, 0, 0",
                   "110, 99, 194",
                   "11, 132, 176",
                   "237, 133, 28",
                   "23, 87, 11",
                   "49, 163, 79")

blackpalette <- sapply(strsplit(blackpalette, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue=255))
bluepalette <- sapply(strsplit(bluepalette, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue=255))
redpalette <- sapply(strsplit(redpalette, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue=255))

blackpalette_five <- sapply(strsplit(blackpalette_five, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue=255))
bluepalette_five <- sapply(strsplit(bluepalette_five, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue=255))
redpalette_five <- sapply(strsplit(redpalette_five, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue=255))

blackpalette_six <- sapply(strsplit(blackpalette_six, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue=255))
bluepalette_six <- sapply(strsplit(bluepalette_six, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue=255))
redpalette_six <- sapply(strsplit(redpalette_six, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue=255))

randompalette <- sapply(strsplit(randompalette, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue=255))


#########################################################################
# Define random colours for plots and theme settings
#########################################################################

random_srv_palette <- c("91, 163, 111",
                        "84, 135, 158",
                        "156, 0, 0",
                        "204, 157, 2",
                        "110, 99, 194",
                        "11, 132, 176",
                        "76, 99, 143",
                        "237, 133, 28",
                        "23, 87, 11",
                        "11, 132, 176",
                        "49, 163, 79")
random_srv_palette <- sapply(strsplit(random_srv_palette, ", "), function(x)
    rgb(x[1], x[2], x[3], maxColorValue = 255))

#########################################################################
# Set plot options
#########################################################################
# Create alternative legend placements inside the plots

legend_bottom_right_inside <- theme(legend.spacing = unit(0.02, "cm"),
                                    legend.background = element_rect(colour = "white", size = 0.1),
                                    legend.key.size = unit(0.5, 'lines'),
                                    legend.justification=c(1,0), 
                                    legend.position=c(1,0))

legend_top_right_inside <- theme(legend.spacing = unit(0.02, "cm"),
                                 legend.background = element_rect(colour = "white", size = 0.1),
                                 legend.key.size = unit(0.5, 'lines'),
                                 legend.justification=c(1,1), 
                                 legend.position=c(1,1))

legend_top_left_inside <- theme(legend.spacing = unit(0.02, "cm"),
                                legend.background = element_rect(colour = "white", size = 0.1),
                                legend.key.size = unit(0.5, 'lines'),
                                legend.justification=c(0,1), 
                                legend.position=c(0,1))

legend_bottom_left_inside <- theme(legend.spacing = unit(0.02, "cm"),
                                   legend.background = element_rect(colour = "white", size = 0.1),
                                   legend.key.size = unit(0.5, 'lines'),
                                   legend.justification=c(0,0), 
                                   legend.position=c(0,0))

#########################################################################
# Create percentage number format settings object for plots
#########################################################################
pct_scale_settings <- scales::percent_format(accuracy = NULL,
                                             scale = 100, 
                                             prefix = "", 
                                             suffix = "\\%",
                                             big.mark = " ", 
                                             decimal.mark = ".", 
                                             trim = TRUE)


#########################################################################
# Define dash types for plots
#########################################################################
#  0 = blank, 1 = solid, 2 = dashed, 3 = dotted, 4 = dotdash, 5 = longdash, 6 = twodash

plt_line_types_5 <- c("solid", "dashed", "dashed", "2222", "2222")
plt_line_types_6 <- c("solid", "dotdash", "dashed", "dashed", "2222", "2222")

#########################################################################
# Define additional plotting theme settings for server data
#########################################################################

theme_srv_extra <- theme_minimal() +
    theme(text = element_text(size=8))+
    theme(axis.text.x = element_text(angle=90, vjust=0.5))


```


<!-- Remove the page number from the bottom of your title page -->

\pagenumbering{gobble}

<!-- Insert your title page as the first thing in the document -->
<!-- Insert your title page as the first thing in the document -->

```{r child = 'titlepage.Rmd'}
```

\newpage

<!-- Set the type of page - to allow for interesting headers and footers -->
<!-- Set the type of page - to allow for interesting headers and footers -->

\pagestyle{fancy}

<!-- Clear all of the positions of the headers and footers, LeftEven, RightOdd -->
<!-- Clear all of the positions of the headers and footers, LeftOdd, RightEven -->

\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}

<!-- Set a line below the header, and an invisible line above the footer -->
<!-- Set a line below the header, and an invisible line above the footer -->

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

<!-- Set the page numbering type for the initial pages of your project -->
<!-- Abstract, table of contents, acknowledgements etc -->

\pagenumbering{roman}

<!-- Create a barrier to stop LaTeX items from floating up above this point -->
<!-- Then start a new page -->

\FloatBarrier
\newpage

<!-- 1. Set the header for the top of the page -->
<!-- 2. Create a section header, but remove the numbering, so that it just shows up as a section -->
<!-- 3. When you remove the section numbering in this way you have to add the section to the table of contents -->
<!-- There is another example in the chapters that is simpler, using the "# Header {-}" structure -->

\fancyhead[CO,CE]{Acknowledgements}
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

<!-- Include the rmd file that you have worked on -->

```{r child = 'acknowledgements.Rmd'}
```

<!-- 1. Again, stop items from floating above this point -->

<!-- 2. This time, the new page option is changed to "cleardoublepage" -->
<!-- This will ensure that the section starts on an odd page number (not necessary) -->
<!-- This is mostly useful if you are writing a book and you want (can just use \newpage)-->
<!-- the chapters all to show up on the right hand page -->

\FloatBarrier
\cleardoublepage

<!-- Set the page header up above your table of contents -->

\fancyhead[CO,CE]{Table of Contents}

<!-- Set how deep you want the table of contents to go -->

\setcounter{tocdepth}{2}

<!-- Insert a table of contents at the beginning of the document -->
<!-- Insert a table of contents at the beginning of the document -->
\tableofcontents
\addcontentsline{toc}{section}{Table of contents}

\cleardoublepage
\FloatBarrier

<!-- Set the page header up above your first part -->

\fancyhead[CO,CE]{Part 1 header for the titlepage and onwards}

<!-- Change the numbering to the standard arabic number set -->

\pagenumbering{arabic}

```{r child = 'part-01-02-titlepage.rmd'}
```

\cleardoublepage
\FloatBarrier

<!-- Set the page header up above your first part -->

\fancyhead[CO,CE]{Guide to supervision}

<!-- Change the numbering to the standard arabic number set -->

\pagenumbering{arabic}

```{r child = 'Guide document.rmd'}
```


\FloatBarrier
\newpage

\fancyhead[CO,CE]{Part 1 header for page - change this, \onlythepage}

```{r child = 'part-01-intro.Rmd'}
```

\FloatBarrier
\cleardoublepage

\fancyhead[CO,CE]{Part 2 title page header for page - change this}


```{r child = 'part-02-02-titlepage.rmd'}
```

\FloatBarrier
\newpage

\fancyhead[CO,CE]{Part 2 header with a page number, \onlythepage}

```{r child = 'part-02-intro.Rmd'}
```

\FloatBarrier
\cleardoublepage

<!-- Change the type of numbering for the lists -->
<!-- Change the type of numbering for the lists -->

\pagenumbering{roman}

<!-- Add a list of all figures -->
<!-- Add a list of all figures -->

\fancyhead[LO,RE]{}
\fancyhead[CO,CE]{List of Figures, \onlythepage}

\listoffigures
\addcontentsline{toc}{section}{List of Figures}

<!-- Add a list of all tables -->
<!-- Add a list of all tables -->

\FloatBarrier
\cleardoublepage

\fancyhead[CO,CE]{List of Tables, \onlythepage}

\listoftables
\addcontentsline{toc}{section}{List of Tables}

<!-- Insert your list of references -->
<!-- Insert your list of references -->

\newpage
\FloatBarrier

\cleardoublepage
\fancyhead[CO,CE]{References, \onlythepage}

# References



