---
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    keep_tex: yes
    dev: tikz
bibliography: bibliography.bib
csl: apa-5th-edition.csl
# csl: cambridge-journal-of-economics.csl
# documentclass: book
classoption: twoside
geometry: 
    top = 25mm,
    left=25mm,
    right=25mm,
    bottom=25mm,
    paperwidth=170mm, 
    paperheight=240mm
urlcolor: black
linkcolor: red
fontsize: 10pt
font-family: times
header-includes:
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \onehalfspacing
- \usepackage{chngcntr}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \counterwithin{equation}{section}
- \counterwithin{footnote}{section}
# - \counterwithin{page}{section}
- \usepackage{subfig}
- \usepackage{float}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \renewcommand{\thepage}{(\thesection):\arabic{page}}
- \newcommand{\onlythepage}{\arabic{page}}
- \newcommand*{\secref}[1]{Section~\ref{#1}}
- \raggedbottom
# - \setlength\parskip{2.5em}
# - \pdfpagewidth 140mm
# - \pdfpageheight 170mm
---

```{r global_options, include=FALSE}

sapply(c("reshape2", "quantmod", "Hmisc", "mFilter", "xtable", "plotrix", "networkD3",
         "Formula", "knitr", "reshape", "plm", "countrycode", "tidyr", "dplyr", "eurostat",
         "plyr", "foreign","ecb", "tidyverse", "stringr", "rstudioapi", "ggplot2", "corpcor",
         "perturb","data.table", "rowr", "statsDK", "date", "kableExtra",
         "readxl", "OECD", "viridis", "fpp", "rsdmx", "roll", "scales", "randomcoloR",
         "grid", "cowplot"), require, character.only = TRUE)

options(knitr.kable.NA = '', knitr.table.format = "latex")

#########################################################################
# Set knitr chunk options
#########################################################################

opts_chunk$set(fig.path = 'figures/',
               echo = FALSE, 
               message = FALSE, 
               warning = FALSE, 
               fig.align = "center", 
               fig.width = 5,
               fig.pos = 'H',
               as.is = TRUE,
               include = TRUE,
               cache = TRUE)

```


<!-- Remove the page number from the bottom of your title page -->

\pagenumbering{gobble}

<!-- Insert your title page as the first thing in the document -->
<!-- Insert your title page as the first thing in the document -->

```{r child = 'titlepage.Rmd'}
```

\newpage

<!-- Set the type of page - to allow for interesting headers and footers -->
<!-- Set the type of page - to allow for interesting headers and footers -->

\pagestyle{fancy}

<!-- Clear all of the positions of the headers and footers, LeftEven, RightOdd -->
<!-- Clear all of the positions of the headers and footers, LeftOdd, RightEven -->

\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}

<!-- Set a line below the header, and an invisible line above the footer -->
<!-- Set a line below the header, and an invisible line above the footer -->

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

<!-- Set the page numbering type for the initial pages of your project -->
<!-- Abstract, table of contents, acknowledgements etc -->

\pagenumbering{roman}

<!-- Create a barrier to stop LaTeX items from floating up above this point -->
<!-- Then start a new page -->

\FloatBarrier
\newpage

<!-- 1. Set the header for the top of the page -->
<!-- 2. Create a section header, but remove the numbering, so that it just shows up as a section -->
<!-- 3. When you remove the section numbering in this way you have to add the section to the table of contents -->
<!-- There is another example in the chapters that is simpler, using the "# Header {-}" structure -->

\fancyhead[CO,CE]{Acknowledgements}
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

<!-- Include the rmd file that you have worked on -->

```{r child = 'acknowledgements.Rmd'}
```

<!-- 1. Again, stop items from floating above this point -->

<!-- 2. This time, the new page option is changed to "cleardoublepage" -->
<!-- This will ensure that the section starts on an odd page number (not necessary) -->
<!-- This is mostly useful if you are writing a book and you want (can just use \newpage)-->
<!-- the chapters all to show up on the right hand page -->

\FloatBarrier
\cleardoublepage

<!-- Set the page header up above your table of contents -->

\fancyhead[CO,CE]{Table of Contents}

<!-- Set how deep you want the table of contents to go -->

\setcounter{tocdepth}{2}

<!-- Insert a table of contents at the beginning of the document -->
<!-- Insert a table of contents at the beginning of the document -->
\tableofcontents

\cleardoublepage
\FloatBarrier

<!-- Set the page header up above your first part -->

\fancyhead[CO,CE]{Part 2 header for page - change this}

<!-- Change the numbering to the standard arabic number set -->

\pagenumbering{arabic}

```{r child = 'part-01-02-titlepage.rmd'}
```

\FloatBarrier
\newpage

\fancyhead[CO,CE]{Part 2 header for page - change this, \onlythepage}
```{r child = 'part-01-intro.Rmd'}
```

\FloatBarrier
\cleardoublepage

\fancyhead[CO,CE]{Part 2 header for page - change this}


```{r child = 'part-02-02-titlepage.rmd'}
```

\FloatBarrier
\newpage

\fancyhead[CO,CE]{Literature Review, \onlythepage}

```{r child = 'part-02-intro.Rmd'}
```

\FloatBarrier
\cleardoublepage

<!-- Change the type of numbering for the lists -->
<!-- Change the type of numbering for the lists -->

\pagenumbering{roman}

<!-- Add a list of all figures -->
<!-- Add a list of all figures -->

\fancyhead[LO,RE]{}
\fancyhead[CO,CE]{List of Figures, \onlythepage}

\listoffigures
\addcontentsline{toc}{section}{List of Figures}

<!-- Add a list of all tables -->
<!-- Add a list of all tables -->

\FloatBarrier
\cleardoublepage

\fancyhead[CO,CE]{List of Tables, \onlythepage}

\listoftables
\addcontentsline{toc}{section}{List of Tables}

<!-- Insert your list of references -->
<!-- Insert your list of references -->

\newpage
\FloatBarrier

\cleardoublepage
\fancyhead[CO,CE]{References, \onlythepage}

# References



